\bf On semidefinite-representable sets over valuation fields

### 2025-05-16 article/paper_padic_spec.tex
commit by Simone

We first give a formal description of our algorithm and then prove its correctness:

\begin{algorithm}
    \caption{SOLVELP($A,b,c,D,e$)}\label{algo_LP}
    \begin{algorithmic}
      \REQUIRE
      $A \in K^{d\times n}$, $b \in K^d$, $c \in K^n$, $D \in K^{m \times n}$ and $e \in K^m$
      \ENSURE [TYPE, $x$], where:
      \vspace{-0.25cm}
      \begin{itemize}
      \item[]
        TYPE $=$ INFEAS and $x=[]$ if and only if \eqref{LP} is infeasible
      \vspace{-0.25cm}
      \item[]
        TYPE $=$ UNBOUND and $x=[]$ if and only if \eqref{LP} is feasible and unbounded
      \vspace{-0.25cm}
      \item[]
        TYPE $=$ FEAS if and only if \eqref{LP} is feasible and has a solution $x$
      \end{itemize}
      \vspace{-0.1cm}
      \hrule
      \vspace{0.1cm}
      \IF{$Dx = e$ has no solution}
      \RETURN [INFEAS, []]
      \ENDIF
      \IF{$D \neq {\bf 0}$}
      \STATE $[\mathrm{STATUS}, y] \leftarrow $
      \RETURN 
      \ENDIF
      %\FOR{epochs = $1$ to $N$}
      %\WHILE{$(j\le m)$}
      %\STATE Randomly initialize $w_i=\{w_1,w_2,\dots,w_n\}$
      %\STATE input $o_j=\{o_1,o_2,\dots,o_m\}$ in the input layer
      %\STATE forward propagate $(f_i\cdot w_i)$ through layers until getting the predicted result $y$
      %\STATE compute $e=y-y^2$
      %\STATE back propagate $e$ from right to left through layers
      %\STATE update $w_i$
      %\ENDWHILE
      %\ENDFOR
    \end{algorithmic}
\end{algorithm}

The first result allows us to consider only iterations of~\eqref{LP} with data of the
form $(A,b,c,0,0)$. When $Dx=e$ has no solution, \eqref{LP} is infeasible, thus
we only consider the case when $Dx=e$ has a solution.

@@

>>>>

We first give a formal description of our algorithm:

\begin{algorithm}
    \caption{SOLVELP($A,b,c,D,e$)}\label{algo_LP}
    \begin{algorithmic}[1]
      \REQUIRE
      $A \in K^{d\times n}$, $b \in K^d$, $c \in K^n$, $D \in K^{m \times n}$ and $e \in K^m$
      \ENSURE [TYPE, $x$], where:
      \vspace{-0.25cm}
      \begin{itemize}
      \item[]
        TYPE $=$ INFEAS and $x=[]$ if and only if \eqref{LP} is infeasible
      \vspace{-0.25cm}
      \item[]
        TYPE $=$ UNBOUND and $x=[]$ if and only if \eqref{LP} is feasible and unbounded
      \vspace{-0.25cm}
      \item[]
        TYPE $=$ FEAS if and only if \eqref{LP} is feasible and has a solution $x$
      \end{itemize}
      \vspace{-0.1cm}
      \hrule
      \vspace{0.1cm}
      \IF{$Dx = e$ has no solution}
      \RETURN [INFEAS, []]
      \ENDIF
      \IF{$D \neq {\bf 0}$}
      \STATE $[\mathrm{STATUS}, y] \leftarrow $
      \RETURN 
      \ENDIF
      %\FOR{epochs = $1$ to $N$}
      %\WHILE{$(j\le m)$}
      %\STATE Randomly initialize $w_i=\{w_1,w_2,\dots,w_n\}$
      %\STATE input $o_j=\{o_1,o_2,\dots,o_m\}$ in the input layer
      %\STATE forward propagate $(f_i\cdot w_i)$ through layers until getting the predicted result $y$
      %\STATE compute $e=y-y^2$
      %\STATE back propagate $e$ from right to left through layers
      %\STATE update $w_i$
      %\ENDWHILE
      %\ENDFOR
    \end{algorithmic}
\end{algorithm}

In order to prove correctness of \Cref{algo_LP}, we proceed step-by-step.
When the system $Dx=e$ has no solution, \eqref{LP} is infeasible and
thus from now on we only consider the case when $Dx=e$ has a solution.

We first prove a reduction result, allowing to consider only iterations
of~\eqref{LP} with data of the form $(A,b,c,0,0)$.

@@

  We conclude with a correctness theorem.

  \begin{theorem} \Cref{algo_LP} is correct.
  \end{theorem}
  \begin{proof}
  \end{proof}
